Scottish Child Poverty Briefing Plots

### 2024-06-03 minos/outcomes/ChildPovReduction_plots.Rmd

```{r}
scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE')
whole_pop_data <- do.call(rbind, generate_df_list('whole_pop', scen.list.test))
```

@@

```{r}
#SF12_change_income_quint <- function(summary_group, scen.list) {

  #summary_group <- paste0(summary_group, '_income_quint')

  print(p1)
  print(p2)
#}
```

>>>>

```{r "SF12_change_num_priority_groups", include=FALSE}
SF12_change_num_priority_groups <- function(scen.list) {

  tit <- 'Number of Priority Subgroups'

  data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))

  data <- replace_na(data, list(num_priority_groups=0))

  plot_data <- data %>%
    select(run_id, num_priority_groups, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
                 names_to = c(".value", "scen"),
                 names_sep = "\\.") %>%
    filter(scen != 'baseline') %>%
    select(-scen)

  plot_data$num_priority_groups <- factor(plot_data$num_priority_groups)

  plot_data_confint <- plot_data %>%
    group_by(year, num_priority_groups) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF_12),
              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  plot_data_confint2 <- plot_data %>%
    group_by(year, num_priority_groups) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF_12),
              margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    labs(title = tit) +
    xlab('Year') +
    ylab('Change in SF-12')

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit) +
    xlab('Year') +
    ylab('Change in SF-12')

  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit) +
    xlab('Year') +
    ylab('Change in SF-12')

SF12_change_percentage_num_priority_groups <- function(scen.list) {

  tit <- 'Number of Priority Subgroups'

  data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))

  data <- replace_na(data, list(num_priority_groups=0))

  plot_data <- data %>%
    select(run_id, num_priority_groups, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ ((. - SF_12.baseline) / SF_12.baseline) * 100)) %>% # Calculate percentage change
    rename_with(~ paste0("percent_change_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("percent_change") | starts_with("mean_cost"),
                 names_to = c(".value", "scen"),
                 names_sep = "\\.") %>%
    filter(scen != 'baseline') %>%
    select(-scen)

  plot_data$num_priority_groups <- factor(plot_data$num_priority_groups)

  plot_data_confint <- plot_data %>%
    group_by(year, num_priority_groups) %>%
    summarise(n = n(),
              mean_SF12_change = mean(percent_change_SF_12),
              margin = qt(0.975, df = n - 1) * (sd(percent_change_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  plot_data_confint2 <- plot_data %>%
    group_by(year, num_priority_groups) %>%
    summarise(n = n(),
              mean_SF12_change = mean(percent_change_SF_12),
              margin = qnorm(0.975) * (sd(percent_change_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    labs(title = tit) +
    xlab('Year') +
    ylab('Change in SF-12')

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit) +
    xlab('Year') +
    ylab('Change in SF-12')

  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit) +
    xlab('Year') +
    ylab('Change in SF-12')

  print(p1)
  print(p2)
}
```

```{r}
#scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
scen.list.test <- c('baseline', 'ChildPovertyReductionABSOLUTE')
whole_pop_data <- do.call(rbind, generate_df_list('whole_pop', scen.list.test))
```

@@

## Number of Priority Subgroups

# TESTING
